\documentclass[12pt,draft]{article}
\begin{document}

\title{PIPO - Peoples Intellectual Property Organization}
\author{Harrison Beau Barker}
\date{}
\maketitle
\begin{quote}
\emph{"The \textbf{P}eoples \textbf{I}ntellectual \textbf{P}roperty \textbf{O}rganization is the name given to the collection of smart contracts governing the fair distribution of copyrights"}
\end{quote}

\begin{abstract}
This document outlines the core functions of the peoples intellectual property organisation including the rights provided by the organisation, the "order of business" and other definitions relating to its operation and interactions with its members.
\end{abstract}

\tableofcontents

\section{Responsibility}
The responsibility of \textbf{PIPO} is to ensure the rights of an authors works indefinitely through registration and ownership disputes of said works. The organisation is not concerned with regulating copyright and intellectual property but instead provides an open and free platform for the application of IP.
\\
\\
\textbf{PIPO's} membership is not dependent on nations involvement or backing and instead holds power and relevance through the participation of people removing an inherent imbalance and distribution of power. Therefore the support and backing of many people is absolutely essential to the success and validity of the organisation.

\section{Rights provided}
\textbf{PIPO} ensures a number of rights to anyone participating in the network, these rights are recognised by the organisation and apply to anyone equally.
\begin{itemize}
	\item The eternal right to original authorship.
	\item The exclusive right to reproduction and the right to authorise any other party for reproduction.
	\item The exclusive right to distribution and the right to authorise any other party for distribution including but not limited to; online distribution markets, public performances or broadcasts.
	\item The exclusive right to adapt and recite work while maintaining all rights to the derivative including the right to seek additional protection on the derivative works.
	\item The exclusive right to alter the underlying ownership of the work including removing the original party as principle owner of the work.
\end{itemize}

\section{Duration of rights}
\textbf{PIPO} takes a blanket approach to this topic by simply stating that any work will be protected for 100 years after the ratification of the work with the organisation.

\section{What is a work?}
A work is defined as the result of a creative endeavour or any activity requiring skill. This does not include the underlying use of language when branding or naming.

\section{Notice of registration}
Once a work has been registered with \textbf{PIPO} a notice of this protection can be displayed.
\\
This can take the form of a simple statement informing that the work has been registered with \textbf{PIPO}:
\begin{quote}
\emph{"This work is registered with The Peoples Intellectual Property Organisation, 00000000-0000-0000-0000-000000000000"}
\end{quote}
This would usually appear next to the already accepted "copyright notice":
\begin{quote}
\emph{"
Copyright © 2021 Harrison Barker. All rights reserved.
\\\\
This work is registered with The Peoples Intellectual Property Organisation, 00000000-0000-0000-0000-000000000000"}
\end{quote}
\subsection{Digital signing}
An author will also be provided with a digitally signed version of their work which will hold the necessary information for displaying registration, this will be in the form of metadata.

\section{Exempt acts}
These acts are exempt from the need for explicit permission from the author prior to use, however this does not provide any protections or defences for the individuals or organisations using these exemptions.
\begin{itemize}
	\item Research.
	\item Incidental inclusion.
	\item Critical review including new reporting.
	\item Any court, legal enquiry or judicial proceedings.
\end{itemize}
When using these exemptions citing or acknowledging the author/rights holder is expected.
\\\\
This document was based on readings from https://copyrightservice.co.uk/copyright/

\end{document}
